---
title: "tial"
author: "KD BAE"
date: '2021 3 23 '
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
1. Draw time series graph of sun spot. Do you see any cycle or seasonal effect?
```{r spotplot}
setwd("C:/Users/Rprogram/Desktop/KD time/time/file")
spot <- read.csv('spot.csv',header = F)
spot <- spot[-1,]
spot <-as.numeric(spot)
x<-1:length(spot)
plot(spot,cex=0.05)
lines(x,spot)
```
**Yes, I see any cycle or seasonal effect!**


2. try 5-point moving average smoothing. Draw the plot of original graph in
black, 5 point MA smoothing in red, mean value in blue.
```{r}
m5=filter(spot,filter=rep(1/5,5))
plot(spot,main="5-point moving average",cex=0.05)
lines(x,spot)
lines(m5,col='red')
abline(h=mean(spot),col="blue")
```

3. Check the residual plot, check the stationary and the test the independence
assumption. Carefully interpret the residual analysis.
```{r}
library(forecast)
res=m5[-c(1,2,99,100)]-spot[-c(1,2,99,100)]
tsdisplay(res,main="Residuals by m5 for spot")
tseries::kpss.test(m5)#h0= TS is stationary
Box.test(res,type="Box-Pierce")#H0= TS is independent
```
**m5 is stationary because p-value not reject H0 in KPSS test **
**,m5 is not independence because p-value reject H0 in Box-Pierce test**
**,1st graph in tsdisplay haven't pattern**
**and On the second and third graph, most of them are in the blue line.**

4. Fit the simple exponential smoothing with alpha=0.1 and with the optimized
alpha. If you think we need a trend, or seasonal, or both try them. Please
address all the moeling and show how you find the best exponential smoothing
model for spot data.
```{r}
h0=HoltWinters(spot,alpha=0.1,beta=F,gamma=F)
h0
h1=HoltWinters(spot,beta=F,gamma=F)
h1

spot1<-filter(spot,filter=rep(1/8,8))
spot1<-spot1[-c(1,2,3,97,98,99,100)]
h2=HoltWinters(spot1,alpha=0.1,beta=F,gamma=F)
h2
h3=HoltWinters(spot1,beta=F,gamma=F)
h3

par(mfrow=c(2,2))
plot(h0)
plot(h1)
plot(h2)
plot(h3)

fa0=forecast(h0)
fa1=forecast(h1)
fa2=forecast(h2)
fa3=forecast(h3)

accuracy(fa1)
accuracy(fa2)
accuracy(fa3)
accuracy(fa0)
```
In the spot graph, I judged that there is no trend but seasonal.
So beta put F and T in gamma, but there was an error that there was no seasonality.
h0,h2 is alpha=0.1
h1,h3 is not alpha=0.1
I put F in both beta and gamma and did 8 point smoothing to remove seasonality from h2,h3.
The result is the same as above and the smallest value of RMSE between h0 and h3 is h3.

5.From your best model, find the forecast of next 4 points.
```{r}
library(forecast)
forecast(h3,h=4)
spot_pred<-predict(h3,n.ahead=4)
spot_pred
plot(forecast(h3,h=4))
```